\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{amsmath}


\usepackage[hmargin=3cm,vmargin=6.0cm]{geometry}
%\topmargin=0cm
\topmargin=-2cm
\addtolength{\textheight}{6.5cm}
\addtolength{\textwidth}{2.0cm}
%\setlength{\leftmargin}{-5cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\evensidemargin}{0.0cm}

\newcommand{\HRule}{\rule{\linewidth}{1mm}}

%misc libraries goes here
\usepackage{tikz}
\usetikzlibrary{automata,positioning}

\begin{document}

\noindent
\HRule \\[3mm]
\begin{flushright}

                                         \LARGE \textbf{CENG 222}  \\[4mm]
                                         \Large Statistical Methods for Computer Engineering \\[4mm]
                                        \normalsize      Spring '2016-2017 \\
                                           \Large   Assignment 3 \\
					
\end{flushright}
\HRule

\section*{Student Information } 
%Write your full name and id number between the colon and newline
%Put one empty space character after colon and before newline
Full Name : Mert Bekar \\
Id Number : 2035749 \\

% Write your answers below the section tags
\section*{A}

I calculated probabilty that more than 25 fishs in this part. I found size with using Monte Carlo study.\\
I looked table A4 for find try number N, so observe that $N = 38416$\\ 
Then, i used $poissrnd$ function to find number of catched fish in three hours,like $poissrnd(12)$(Poisson Number = 4, time = 3 hours)\\
Afterwards, i calculated weight of one fish with rejection method and i done this calculation $poissrnd(12)$ time. In this moment, i have total weight for one try and i could decide total weight bigger than 25 kg or not. I save all bigger conditions.\\
Then, i calculated this process 38416 time. I summed all total weight for all tries.\\
Finally, i found probabilty with dividing number of all bigger condition with number of all tries(38416).




\section*{B}

I have founded all total weight in part A.\\
I divide all total weight to number of tries(38416) and i obtain average easily.\\



\section*{C}

For calculate standard deviation, i save weight of all tries one-to-one in array. I summed all difference of average from array elements one-to-one. I find squrate root of sum/(n-1) where n-1 = 38415. So, i obtained standard deviation. 


\end{document}

